---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(nms4r)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```

## Rendering modal windows

In order to render a single modal window from R markdown to html, use the function  [generate_html_4_rmd()](../reference/generate_html_4_rmd.html). The function expects the full path of the R markdown file to be rendered, such as in the following example:

```
generate_html_4_rmd(here::here("modals/tar.Rmd"))
```

To render all R markdown files in the "modals" directory to html, the 
function to use is [render_all_rmd()](../reference/render_all_rmd.html). The 
R markdown files that need to be re-rendered most frequently contain interactive elements,
as the data those elements draw from are frequently updated. Consequently, the function
has the option of just re-rendering R markdown files that contain interactive elements

```
# Render all R markdown files in the modal directory
render_all_rmd("cinms")

# Render R markdown files in the modal directory that have interactive elements
render_all_rmd("cinms", interactive_only = T)
```

## Displaying the latest data

Satellite-derived data is displayed in several of the modal windows, such as in the following example:

```{r sst_time_series, echo=FALSE}
nms4r::plot_metric_timeseries("https://raw.githubusercontent.com/marinebon/cinms/master/data/oceano/statistics_sst_cinms.csv", "sst")
```

This data and the resulting figures are auto-updated every month by calling **nms4r** functions in Github Actions. In the case of the Channel Islands National Marine Sanctuary, the file that controls these actions can be found [on GitHub here](https://github.com/marinebon/cinms/blob/master/.github/workflows/update-oceano.yml).
