---
title: "Plotting Functions"
author: "Tylar Murray"
date: "2017-07-20"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plotting Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Infographiq attempts to choose default plotting functions automatically, but
there are times when you want to plot in a specific way.
The (optional) `plotting_function_call` column in `plot_indicators` can be used
to tell infographiq how to plot the data for each indicator.

`plotting_function_call` can be set to:

1. nothing, allowing infographiq to use defaults.
2. a "magic string" that infographiq can recognize and know what to do.
3. an R function call.
4. a filepath to a brew template

## Using "magic strings"

These magic strings roughly align with the plotting function brew templates in
`./inst/site_template/plotting_functions/`.

* "plot_none" :
Create no plot for this indicator.
Useful if you just want captions.
* "embed_html" :
use a pre-made, externally-hosted html plot.
URL to the html file is passed in the `csv_url` column in place of URL to a csv file.
* "include_graphic" :
use a pre-made jpg, png, or other image.
URL to the image is passed in the `csv_url` column in place of the URL to csv file.
* "plot_dygraph_timeseries" :
Creates an interactive timeseries plot using dygraph.
This is the current default behavior if `plotting_function_call` is empty or `NA`.

## Using R Function Calls

R code can be put directly into the `plotting_function_call` column.
Code should be wrapped in quotes and quotes within the code must be doubled ("").
Any arbitrary R code can be executed in this way and the output will be put in the modal.
Examples :

* `"print(""This is my custom plotter code all shoved into a single column directly in the csv file AND a bunch of commas: ,,,,,a,b,c,123,,,!"")"`
* `"plot_dygraph_timeseries(csv_tv='https://raw.githubusercontent.com/marinebon/info-fk/master/prep/data/rvc_trophic_groups/lionfish_bio.csv', title='Lionfish Biomass', y_label='Mean Biomass (g/40Mm^2)', col_t='YEAR', col_y='biomass_mean', std_err='biomass_se')"`

# Using brew templates
Cramming code into csv columns is ugly, so you can put R code into a brew template file and the pass the filepath in the `plotting_function_call` to create a custom plot at site-build-time.

As an example, consider we have the following brew template file in "/home/me/my_custom_plotting_function.rmd.brew":

```
    My Custom Plot : <%=plot_title%>
    -----------------------------
    I can put [markdown](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet) formatting here.

    Also I can execute R code and see the result in the modal.

    ```{r}
    # in this file we use a custom plotting method to plot data from the
    # csv_url. These comments within the R block won't show up in the output.

    print("loading data from <%=csv_url%> ...")
    print("...just kidding, let's use fake data to keep this simple.")

    # Define the vector with 5 values
    my_data <- c(1, 3, 6, 4, 9)

    # output my custom graph
    barplot(my_data)
    print ("<%=plot_caption%>")

    print("I can use the columns from plot_indicators using brew template formatting.")
    print("svg id is <%=svg_id%>")
    print("<%=col_t%> vs <%=col_y%>")
    ```
```

We can put /home/me/my_custom_plotting_function.rmd.brew in the `plotting_function_call` column and the output will be rendered into the modal.
Note the variables available in the rendering context of the brew template:

* csv_url
* svg_id
* col_t
* col_y
